THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. These had 
eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was discovered in 1995 
in the Tevatrón collider of the Fermilab laboratory, this proton collider operated with an energy of 1.8 TeV at the center of mass up to 
2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 colliding protons at 7 TeV and then 
at 8 and 13 TeV.

>>>>

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. These had 
eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was discovered in 1995 
in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass energy of 1.8 TeV untill 
2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 colliding protons at 7 TeV and then 
at 8 and 13 TeV.
